---
title: "PracticalMachineLearning"
author: "Jun Imamura"
date: "May 25, 2015"
output: html_document
---

***
# Synopsis
This document analyzes personal activity data obtained from activity sensor. The data's specification is described [here]("http://groupware.les.inf.puc-rio.br/har").
***

# Include Library and Download Dataset
```{r, library, warning=FALSE}
library(caret)
library(DMwR)
library(randomForest)
```


Download data from server and extracts them to variables called trainDat and testDat.

```{r, dataLoading, cache=TRUE}
urlTrain <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
urlTest <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
download.file(urlTrain, destfile="./traindat.csv", method="curl")
download.file(urlTest, destfile="./testdat.csv", method="curl")
trainDat <- read.csv("./traindat.csv", na.strings=c("NA", "#DIV/0!"), stringsAsFactors = FALSE)
testDat <- read.csv("./testdat.csv", na.strings=c("NA", "#DIV/0!"), stringsAsFactors = FALSE)
```

You can see some data are almost lost. There are so many covariates which is mostly consisted of NAs. In this time, I've decided to omit such a variable because it can rarely be useful for current practice.

```{r, ignore}
trainDat$classe <- as.factor(trainDat$classe)
## See the data has too many NA values
unique(colMeans(is.na(trainDat)))
## Delete covariates which is mostly consist of NA values
trainDat <- trainDat[, colMeans(is.na(trainDat))< 0.9]
```

Next, split data into training set and testing set. Testing set is used as a cross-validation set at this time.
```{r, splitData}
inTrain <- createDataPartition(y=trainDat$classe, p = 0.75, list=FALSE)
# omitting undesiable variables
training <- trainDat[inTrain, 8:60]
testing <- trainDat[-inTrain, 8:60]
```

I used machine learning method "random forest" for modeling. This method is well known because of its performance.
```{r, randomForest}
model <- randomForest(classe~., data = training)
mean(predict(model, newdata=testing[,-53])==testing$classe)
```

It seems working in very good accuracy.

***

# Conclusion
In this document, personal activity data was investigated using machine learning algorithm, and random forest algorithm could achieved very good performance.